Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
Work on explaining the algorithm.

@@

\todo{Explain the algorithm with pseudocode?}

>>>>

\todo{``Suggest'' can also be used to trigger recovery}.

@@

\todo{Explain the algorithm with pseudocode?}
Local variables: committed, a map from commands to dependency sets, initially the empty map.
\begin{itemize}[noitemsep,nolistsep]
    \item Upon ${propose\left( c \right)}^p$: call ${announce\left( c \right)}^p$.
    \item Upon ${suggest\left( c,d \right)}^p$: call ${propose\left( c,d \right)}^p$.
    \item Upon ${decide\left( c,d \right)}^p$: insert the mapping $c \rightarrow d$ in the map ``committed''.
    \item Periodically: process the committed commands, as described below.
\end{itemize}

The variable ``committed'' of the algorithm above can be seen as describing a directed graph $g$ whose vertices are commands and such that there is an edge from $c_1$ to $c_2$ if and only if ``committed'' maps $v_1$ to a set $deps$ where $v_2\in deps$, i.e. $v_1$ depends on $v_2$.
